Detecting Facial Expressions in Professional Tennis Matches

### 2016-12-20 Report06-12.Rmd
removed hard link, changed authorship

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: Stephanie Kobakian, Mitchell O'Hara Wild. Supervised by Dianne Cook, Stephanie
  Kovalcik
date: "November 19 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: yes
  word_document:
    toc: yes
fontsize: 11pt
bibliography: references.bib
---

@@

setwd("C:/Users/steff/Github/face-recognition")

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: Stephanie Kobakian, Mitchell O'Hara Wild, Stephanie
  Kovalcik, Dianne Cook
date: "November 19 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: yes
  word_document:
    toc: yes
fontsize: 11pt
bibliography: references.bib
---

@@

#setwd("C:/Users/steff/Github/face-recognition")
